\subsection{Derivatives}

Let $f(x)$ be any continuous function and let $a, b$ be two points in the domain of $f$ with $a\leq b$. The \emph{rate of change in $f$ from $a$ to $b$ is the speed that $f$ changes over the interval $[a,b]$} and is measured by the slope of the line between
the points $(a, f(a))$ and $(b, f(b))$
\begin{equation}\label{eq:pre roc}
    \frac{f(b)-f(a)}{b-a}.
\end{equation}
This is also the line running tangent to these points.
As an example of this, let $f(x)=x^2$. Our rate of change for $a=0$ and $b=1$ would then be 1, and if we instead set $a=1$ and $b=2$, the rate of change comes out as 3. This makes sense since at $a=1$, $f$ is rising faster than at $a=0$. By minimizing the distance between $a$ and $b$, we get a better estimation for our rate of change, since narrowing this margin reduces any smoothing that occurs in bigger margins. For an idea of this, take $a=-2$ and $b=2$. Then our rate of change is $0$, which does not seem accurate since at $f(a)$ we are reducing the speed which we move down and so we would expect our rate of change to be negative. If we instead set $b=0$, we have a rate of change of -2, which seems more accurate considering the graph of $x^2$ bottoms out when $x=0$. As such, the negative value for $f(a)$'s rate of change tells us that the rate that $f(x)$ decreases between -2 and 0 is decreasing i.e., the change in $f$ is slowing down.

Keeping this in mind, we instead want to examine the affect of closing the margin $b-a$, and so it is much more convenient to change the notation to reflect this. Let $x_1 = a$ and let $h = b - a$. Equation (\ref{eq:pre roc}) can then be simplified to
\begin{equation}\label{eq:roc}
    \frac{f(x_1+h)-f(x_1)}{h}.
\end{equation}.

We then get the \emph{instantaneous rate of change of $f$ at $x_1$} by
narrowing the offset $h$ in Equation (\ref{eq:roc}) to an infinitely small
amount, nearly 0, at $(x_1, f(x_1))$.
\begin{equation}\label{eq:iroc}
    \dx[f] (x_1) = \lim_{h\rightarrow 0} \frac{f(x_1 + h) - f(x_1)}{h} \quad .
\end{equation}
This is otherwise known as the slope of the line that runs tangent to the \emph{point} $(x_1,f(x_1))$. The instantaneous rate of change can be thought of as finding the direction that $f$ is moving in at the exact point $x_1$.

By extrapolating Equation (\ref{eq:iroc}) to the rest of $f$'s domain, we define \emph{the derivative of $f$ with respect to $x$ as the
instantaneous rate of change for all $x$ in the domain of $f$}
\begin{equation}\label{eq:derivative}
    \dx[f] (x) = \lim_{h\rightarrow 0} \frac{f(x + h) - f(x)}{h} .
\end{equation}

We will use a couple of alternate notations for the derivative
throughout the text
\begin{equation*}
    \dx[f](x) \quad \text{or} \quad \dx f(x) \quad \text{or} \quad f'(x)
\end{equation*}, all of which represent the derivative of a function $f$ with respect to its input, $x$.


% TODO: Add more here
% Include specifications on the variable with which the differentiation is in
% respect of i.e. dx or dy or what not

We will now define the nine rules by which most differentiation can be performed. Let $c$ be a constant, let $x$ and $y$ be variables, and let $f(x)$ and $g(x)$ both be continuous and real valued functions.

\begin{psec}{Constants}\label{rule:derivative constants} For constants,
    we have
    \begin{equation}\label{eq:derivative constant}
        \dx c = 0
    \end{equation}
    . This is an intuitive consequence since a constant by definition does not
    change, and thus has no rate of change.

    If we differentiate a variable that does not change with respect to changes in our differentiating variable, then its derivative is treated as a constant. The same applies to a function. So when the variable $y$ or the function $h(y)$ are unaffected by or otherwise independent of changes in $x$, both have the derivatives
    \begin{equation*}
        \dx y = 0, \quad \quad \dx h(y) = 0.
    \end{equation*}

\end{psec}

\begin{psec}{Power rule}\label{rule:derivative powers} The rate of change for a variable with a constant power is defined in terms of the precedent power
    \begin{equation}\label{eq:derivative power}
        \dx x^{c} = c x^{(c - 1)}.
    \end{equation}
    To understand this, consider two cases
    \begin{align*}
        f(x) &= x &\quad \dx[f](x) &= 1,\\
        g(x) &= x^2 &\quad \dx[g](x) &= 2x.
    \end{align*}
    For the case of $f(x)$, the derivative tells us that the function monotonically increases at a constant rate. For $g(x)$, we find that the rate of change is still dependent on $x$, so its rate of change is no longer constant and changes based on its point in the domain. For $x<0$ we see that $\dx[g]$ is negative and so the rate of change in $g$ is decreasing. Likewise, when $x>0$, $g(x)$'s pace is increasing.

\end{psec}

% TODO: Cover polynomials in here
\begin{psec}{Addition and subtraction}\label{rule:derivative add} The derivative of a sum is the sum of its derivatives
    \begin{equation}\label{eq:derivative add}
        \dx (f(x) + g(x)) = \dx[f](x) + \dx[g](x).
    \end{equation}
    We can extend this rule to include the summation of more than two numbers as well. For the summation of $n$ functions indexed by $f_i(x)$ for $1\leq i\leq n$, the derivative is given by
    \begin{equation}\label{eq:derivative n add}
        \dx\left(\sum_{i=1}^{n} f_i(x)\right) = \sum_{i=1}^{n} \dx[f_i](x)
    \end{equation}

\end{psec}

\begin{psec}{Product rule}\label{rule:derivative product}

    \begin{equation}\label{eq:derivative prod}
        \dx \left(f(x)*g(x)\right) = \dx[f](x) *  g(x) + f(x) *
        \dx[g](x)
    \end{equation}

\end{psec}

\begin{psec}{Chain rule}\label{rule:derivative chain}

    \begin{equation}\label{eq:derivative chain}
        \dx (f \circ g)(x) = \diff{f}{g} * \diff{g}{x}(x)
    \end{equation}

\end{psec}

\begin{psec}{Quotient Rule}\label{rule:derivative quotient} The quotient rule is just an extension of the
    power, product, and chain rules.
    \begin{equation}
        \dx \left(\frac{f(x)}{g(x)}\right) = \frac{\dx[f](x) * g(x) - f(x) * \dx[g](x)
        }{g(x)^2}
    \end{equation}.

\end{psec}

\begin{psec}{Exponent rule}\label{rule:derivative exponent}

    \begin{equation}
        \dx \ln(f(x)) * c ^ {f(x)} = c ^ {f(x)} * \dx[f](x)
    \end{equation}

\end{psec}

\begin{psec}{Logarithm rule}\label{rule:derivative log}

    \begin{equation}
        \dx \log_c f(x) = \frac{1}{\ln c} * \frac{1}{f(x)} * \dx[f] (x)
    \end{equation}

    For the natural log, this is simplified to
    \begin{equation*}
        \dx \ln f(x) = \frac{1}{f(x)} * \dx[f].
    \end{equation*}

\end{psec}


\begin{psec}{Trigonometric rules}


\end{psec}
